### 2019-05-16 thesis.tex
* thesis.tex: Summary: Still editing the introduction

nature, of the charged particles, overcome the influence of the binary collisions
between neutral particles on the overall dynamics of the gas. The charged particles
might also interact with the neutral components of the gas

>>>>

nature, of the charged particles, overcome the influence of the neutral-neutral
and neutral-charged binary collisions, on the overall dynamics of the gas. As a
consequence of the long-range feature of the electric and magnetic fields, one
charged particle may interact with several other particles, that interface with
other charges, and so on; characterizing the so-called ``collective behavior''.
Such behavior gives rise to a variety of plasma waves and instabilities, whose
intensities will depend on another essential collective property of the plasma:
the Debye shielding. The Debye shielding is defined as the resulting net charge
inside a given volume element of the plasma. When the number of negative and
positive particles are the same, the plasma waves and instabilities arise from
the small fluctuations driven by the constant movement and interactions among the
charges. These small fluctuations on the Debye shielding establish a fundamental
characteristic of neutral plasmas, the ``quasineutrality''. On the other hand,
plasmas that do not have overall charge neutrality might also have some degree
of Debye shielding. In such case, however, the electric and magnetic fields are
more intense and have a longer range due to the absence of quasineutrality.
These characteristics make nonneutral plasmas a whole new subject, with distinct
properties regarding its behavior and stability.
